\subsubsection{Problems}


\subsubsection{Proposed Solutions}


\subsubsection{Reflections}


\subsubsection{Meetings}

    There was only the scheduled Monday meeting with our supervisor.

\subsubsection{Interim Goals}


\subsubsection{Description of Individual Performance}
    \begin{itemize}
      \item \performance{\martin}{
        This week I mainly focused on reworking more of the performance system as a whole. This took more time/did not make much improvements than anticipated because there were other unrelated bugs messing with the code.
      }
      
      \item \performance{\felix}{
        Did not contribute to the project this week due to exam week in optional course and the course that runs parallel for IT-students. 
      }
      
      \item \performance{\hannes}{
        This week I mainly worked on connecting roads to each other. I also finished the visual navigation path and did some traffic light work.
      }
      
      \item \performance{\marcus}{
        This week I mostly worked on bug fixes and multi lane navigation support. I also added support for multiple independent road systems as well as finished intersection navigation. I also created a demo scene in preparation of the demonstration for our supervisor at our weekly meeting.
      }
      
      \item \performance{\jakob}{
        I started this week working on fixing some bugs. An example, was that the intersection flow containers that take care if an intersections road signs, would overflow spawn them, resulting in duplicate game objects. Additionally, I implemented a script that handles in game time, as well as a basic schedule for events. The schedule is built using a calendar queue, that prioritizes the events by their respective time stamps.
      }
    \end{itemize}
