\subsubsection{Problems}
    Main problems this week took the form of making our modified third-party assets handle intersections, and setting up a Unity to organization to allow future asset purchases to be available for the whole group. 

\subsubsection{Proposed Solutions}
    The proposed solution for solving the Unity Asset situation is for one group member to do proper research to find the most efficient way for group asset managing. To solve the intersection problems, it was decided to have every group member test the lane creation on their own computer since the results seem to wary between group members.

\subsubsection{Reflections}
    Overall a good first development week, still some hick-ups regarding different set up of varying tools. Since we started working early on the project plan we've had to receive feedback from the supervisor two times already. 

\subsubsection{Meetings}
    Supervisor meeting and numerous remote in-official developer meetings throughout the week

\subsubsection{Interim Goals}
    We sent in our draft of the project plan to our supervisor and received feedback as planned. The goals for this week's sprint were mostly met, however the features were developed in separate branches so they will need to be merged together in order to create a working version that includes all the new features.

    The goals for next week are based around our goal for the first iteration, which is to have working autonomous vehicles. Next week we will for example implement algorithms for lane switching so that the vehicles can transfer between different lanes and also roads through intersections.

\subsubsection{Description of Individual Performance}
    \begin{itemize}
      \item \performance{\martin}{
        I have done a lot of exploration of assets and testing their compatibility with the current version of unity (and sharing them). I was also meant to do the road networks for testing but ran into problems/bugs with road architect. Road architect now needs further evaluation of functionality before work can precede. Lastly I polished my sections in the planning report and did my usual duties as the secretary.
      }
      
      \item \performance{\felix}{
        Did some further modifications of the scrum board. Had a lot of issues with git and different development set up but should be mostly fixed now. Implemented a player controlled car that the player control via keyboard. Reviewed feedback and added new text to Problem, Method and Ethical Considerations in the project plan. 
      }
      
      \item \performance{\hannes}{
        I have mainly worked on graph generation this week. I added a weighted graph representation from a road architect road system. I developed a graphical debug view for the graph that clearly shows how all roads are connected. I also wrote an A* implementation that can find the shortest path to a node. 
      }
      
      \item \performance{\arvid}{
        
      }
      
      \item \performance{\marcus}{
        I have worked on improving the lane generation by making it support intersections as well as looped roads. Furthermore I have supported in the development of creating a road network graph to allow the vehicles to navigate. Finally, I implemented two algorithms for making the vehicles follow lines. One that works using physics and vector arithmetic to steer towards the line, and a more performance optimised version that simply moves the vehicle between the points on the line.
      }
      
      \item \performance{\jakob}{
        My main focus this week was to implement a camera switching system. The system I created allows the user to map cameras to key binds, as well as UI overlay buttons that will change the users POV. This UI is also the basis we'll use to implement a future development UI. After finishing this, I started looking into Blender, which I thought was a good tool to use to create road signs etc for the project. However, after creating some road signs, we found an asset that included all European road signs, as well as an editor for them which we decided to use instead. Lastly, I also spent some time cleaning up my sections in the planning report.
      }
    \end{itemize}