\subsubsection{Problems}
During the first week no major problems were encountered.
\subsubsection{Proposed Solutions}
-
\subsubsection{Reflections}
The team feels that they have sufficient guidance in which tool to investigate for the product development. Each and everyone also feels satisfied with being assigned a static role throughout the whole project.
\subsubsection{Meetings}
An introduction meeting was held the first day of the course, as well as a secondary meeting to do some general planning and work-assignment. The first meeting with our supervisor was held 
\subsubsection{Interim Goals}
Everyone should familiarize themselves with the relevant tool we are using and the protocols and tools related to their specific role within the project.  
\subsubsection{Description of Individual Performance}
    \begin{itemize}
      \item \performance{\martin}{I spent my time mostly looking at tutorials and getting to know Unity. I also worked on fixing templates for documentation since i have the role of Secretary.}
      
      \item \performance{\felix}{Brushed up on my Scrum knowledge since I was assigned as the team's Scrum Master. Also installed necessary tools and did some "Hello World" projects of varying difficulty in Unity.}
      
      \item \performance{\hannes}{ This week I mainly watched unity tutorials. }
      
      \item \performance{\arvid}{}
      
      \item \performance{\marcus}{I focused on administrative tasks such as preparing the time report and setting up a CI/CD for autocompilation of LaTeX documents. In addition to that I setup a document structure in Overleaf}
      
      \item \performance{\jakob}{This past week I spent my time mostly on getting to know Unity. For example, I made a simple program where the user can move around on a flat surface, as well as jump. Furthermore, I spent some time in Overleaf, creating a template for the weekly logbook.   }
    \end{itemize}
