\subsubsection{Problems}
    We have not encountered any problems yet, however our supervisor noted that we might get a lot of merge conflicts in the future since we are working in the same Unity project.

\subsubsection{Proposed Solutions}
    Our supervisor recommended that we create one scene in Unity for each developer and that all developers work solely in their own scene to avoid merge conflicts. We setup the Unity project like this with an additional main scene where we will put the result itself.

\subsubsection{Reflections}
The team feel more confident in being able to use Road Architect as a tool for drawing our maps, which led to the whole team investing more time in understanding how it works. 

\subsubsection{Meetings}
We had a supervisor meeting and a planning and setup meeting. 

\subsubsection{Interim Goals}
We set our first product development sprint goal, "Enable one car to follow lanes in two simple road maps". We also set a goal to be able to send in the first draft of our project plan to our supervisor early this week for feedback. 

\subsubsection{Description of Individual Performance}
    \begin{itemize}
      \item \performance{\martin}{
        This week I spent my time mainly on writing in the project report, collecting relevant data from sources and exploring Unity further. 
      }
      
      \item \performance{\felix}{
        This week I wrote on the Problem and Method section of our project plan, read a lot of papers regarding relevant topics for our product. Familiarised myself with the Unity asset Road Architect and set up my development environment for Unity (VC, IDE integration, etc). 
      }
      
      \item \performance{\hannes}{
        This week i mainly wrote on the project plan, specifically the problem section. I also started getting familiar with the road architecture source code and coded a little bit.
      }
      
      \item \performance{\arvid}{This week I was quite busy with other things so I haven't been able to put down the work I intended. I acquainted myself with the course a little bit more and started working on societal and ethical aspects in the project plan. On Friday I participated in the meeting.}
      
      \item \performance{\marcus}{
        I continued with some administration and setup of our documentation, but spent most of my time looking into the Road Architect asset. We have looked into this asset briefly since it allows us to create road systems easily. It is also very powerful with support for creating intersections and bridges for example as well as modify the terrain.

        I looked into the development possibilities for the asset since we need additional features such as creating lines for each lane that we need to use for our vehicles as a guide line that they should follow while driving. I was able to add that feature to the asset and figured out more of how it works so I now feel confident that we can use Road Architect in our project.
      }
      
      \item \performance{\jakob}{
        I spent my time about 50/50 between writing the project planning report and doing research about Unity. During the research I found out about tools like Unity's UI Toolkit and Unity's New Input system. 

        To test these features I created a 2 simple Unity projects. The first project allows the user to move around as a rolling cube, which I made to test the input system. The second project was a very simple UI using the toolkit.

        For the project planning report, it was decided that I should write the purpose and limitation sections, which I completed.
      }
    \end{itemize}
