\subsubsection{Problems}


\subsubsection{Proposed Solutions}


\subsubsection{Reflections}

    The midterm presentation was held during this week. From the presentation we got some input from the audience about certain aspects of the project. The main point that was brought up, was that since we declared that our simulator will be user-friendly, we need to complete the necessary testing to prove this claim.

\subsubsection{Meetings}

    There was only the scheduled Monday meeting with our supervisor.

\subsubsection{Interim Goals}

    Hopefully complete a first stable build release of the project that can be used to demo.


\subsubsection{Description of Individual Performance}
    \begin{itemize}
      \item \performance{\martin}{
        This week I mainly focused on the half time presentation but also did some work (Bug fix and rework some logic) on performance mode in AutoDrive and some finishing touches on the node occupancy system. 
      }
      
      \item \performance{\felix}{
        Apart from the half time presentation, I havent contributed to the project this week due to exam and hand ins in two other courses. For some reason, IT student take 2.5 courses LP3 and 1.5 in LP4!
      }
      
      \item \performance{\hannes}{
        This week i created speed sign spawning, disabled u turns, traffic light stop logic and road spawning using OSM data.
      }
      
      \item \performance{\marcus}{
        I worked a lot with turning in intersections this week, as it is a more difficult task than it seems. There was a lot of work trying to create the different paths the vehicle can take depending on which road it enters in and should exit at in an intersection. The paths need to be separated so the vehicles do not affect each other, except for the occupation feature where it is important that they share the data so they are aware of other vehicles travelling in the intersections.

        I also created a debug utility that allows us to draw lines, and place spheres at positions to visualize where points are in space to help with debugging.
      }
      
      \item \performance{\jakob}{
        Because of personal reason, I haven't spent that much time on the project this week. But even so, I managed to implement and connect a UI overlay for the simulator. The functionality of the UI works, but the buttons need to be connected to their functions. The UI overlay has a very simple design, since the style sheet for the simulator has been decided.
      }
    \end{itemize}
