\subsubsection{Problems}


\subsubsection{Proposed Solutions}


\subsubsection{Reflections}


\subsubsection{Meetings}

There was only the scheduled Monday meeting with our supervisor.

\subsubsection{Interim Goals}


\subsubsection{Description of Individual Performance}
    \begin{itemize}
      \item \performance{\martin}{
        This week I did not have much time due to moving living location. But I managed to at least do some PR reviews and switched the distance calculation logic for the car. As well as some report writing and a small start to the node occupation model.
      }
      
      \item \performance{\felix}{
        Researched related work, read up on papers regarding these. Compared them to each other and wrote about them in the project plan report. Did some further coding on input handling and cameras.
      }
      
      \item \performance{\hannes}{
        This week i wrote on the final report on the theory and method. I also implemented the navigational system for the cars. Now the cars can travel to a given position.
      }
      
      \item \performance{\marcus}{
        My main focus this week was finishing intersection creation. I added support for 3-way intersections, and switched all intersection generation to procedural mesh generation, meaning they are dynamically created and create a good transition between roads allowing intersections to be created for different road angles.
      }
      
      \item \performance{\jakob}{
        I spent my time working on two things this week. To begin, I wrote some sections on the first draft of the final report. Specifically, I wrote the tools section in the methods chapter. Programming wise, I implemented a car spawner object that spawns the cars when the program is started. The user can change in the settings how many cars should be spawned, and the script will divide them between the roads by the length ratio of the road. Or, you can spawn an amount of cars based on the roads max capacity of cars. Each car is automatically offset an equal amount between each other so no collisions take place. With the car spawner, I was also able to some limit testing on how many cars we would be able to have running at the same time.
      }
    \end{itemize}
