\subsubsection{Problems}


\subsubsection{Proposed Solutions}


\subsubsection{Reflections}

    During the meeting we decided on dividing up the remaining work. Marcus and Hannes will implement point of interests for the vehicles, and improve the navigation. Felix and Martin will work on the UI by adding more features, and improve the design. Lastly, Jakob will continue on the car spawner, and increase the amount of vehicle types in the simulation.

\subsubsection{Meetings}

    The only meeting was the regular scheduled supervisor meeting on Monday.

\subsubsection{Interim Goals}


\subsubsection{Description of Individual Performance}
    \begin{itemize}
      \item \performance{\martin}{
        This week I was away for the most part but I did some work on UI. I implemented draggable windows, expanded on the functionality a bit with another statistics window and looked at some design options.
      }
      
      \item \performance{\felix}{
        Only wrote on the report this week (theory and introduction section). Produced around 10 pages. 
      }
      
      \item \performance{\hannes}{
        This week I worked on generating cities from OSM data. I added road spawning, building spawning and added bus stop spawning. I also wrote a bit on the city generation section.
      }
      
      \item \performance{\marcus}{
        After planning and dividing the work for the upcoming weeks I have focused on POIs, such as homes and parkings. These will then be used as targets for the vehicles to simulate realistic traffic flows. Some of them, such as parkings, will also be interactive so the cars can park there and after a while exit the parking and once again join the traffic.
      }
      
      \item \performance{\jakob}{
        During our weekly meeting we decided to divide the remaining work between the group members. My task was to increase the amount of vehicle types in the simulator, and implement the required changes to car spawner which is what I spent my time on. I was abroad between Thursday and Sunday, so I did all the work in the beginning of the week, which explains my time report. 
      }
    \end{itemize}
