\subsubsection{Problems}


\subsubsection{Proposed Solutions}


\subsubsection{Reflections}


\subsubsection{Meetings}

    The only meeting was the regular scheduled supervisor meeting on Monday.

\subsubsection{Interim Goals}


\subsubsection{Description of Individual Performance}
    \begin{itemize}
      \item \performance{\martin}{
        This week I mainly worked more on the UI doing various things such as styling, moving/removing/adding functionality. I also implemented scene switching and improved the menu scene.
      }
      
      \item \performance{\felix}{
        Worked on references, fixed corrupted branch and merged data gatherer code, read feedback from librarian and adjusted text. Also extended som sections in introduction and method.
      }
      
      \item \performance{\hannes}{
        This week I worked on POI navigation, Intersection mesh, OSM and UV setup for roadside parking.
      }
      
      \item \performance{\marcus}{
        This week revolved around trying to get many different parts working together, so I did work in several different areas. I focused on bus stop and parking POIs, and I also added support for intersections with yielding signs instead of traffic lights.
      }
      
      \item \performance{\jakob}{
        This week I worked on multiple different areas of the simulation. I finished the roof algorithm for OSM using an ear clipping method. I added a day/night cycle to the simulation to improve it's reflection on real-life. I rigged all the new vehicles with brake lights and indicators. Lastly, I started designing the world for the Masthugget build.
      }
    \end{itemize}
