\subsubsection{Problems}


\subsubsection{Proposed Solutions}


\subsubsection{Reflections}

    Because of the due date for the first hand-in of the report, as well as our upcoming scheduled fackspråk 2 meeting, a lot of time this week was spent on the report. Multiple new sections were written in all sections excluding the results and discussion chapters. These chapters will be written in the upcoming weeks due to the simulation not being finished yet.

    On the simulation side of the project, many new features were added. These features include OSM-imports, point of interests, an updated UI, and displayed road occupancy statistics.

\subsubsection{Meetings}

    The only meeting was the regular scheduled supervisor meeting on Monday.

\subsubsection{Interim Goals}


\subsubsection{Description of Individual Performance}
    \begin{itemize}
      \item \performance{\martin}{
        This week I worked on improving the visual look of the UI and looked into implementing graphs for statistics. We noticed a compatibility issue with our graph asset and we'll try to work around it by running two UI systems in parallel.
      }
      
      \item \performance{\felix}{
        Worked on references for the project report. Worked on gathering and displaying statistic, as well as shaders to signal different colors on the road when things like congestion changes. 
      }
      
      \item \performance{\hannes}{
        This week I added one-way roads, fixed the intersection mesh with proper UV setup, added lines and traffic signs according to traffic rules. I also added tree generation from OSM data. I also started working with the POI navigation system.
      }
      
      \item \performance{\marcus}{
        This week I focused on developing the POI system we need for the different places the vehicles need to visit. I started working on homes, fuel stations and parkings and the navigation needed for the vehicles to find their way between them. I also spent time writing on the report, about how the vehicles drive and the code review we have for each PR. I also fixed the structure and formatting of the report.
      }
      
      \item \performance{\jakob}{
        This week was spent on finishing my sections in the methods chapter for the assignment due date. The three main sections I wrote were: Quality vs Performance, Optimizations, and UI design. On the programming side of the project, I worked on the OSM import system that we've created, specifically getting the roofs to appear. To solve the issue, I had to implement an algorithm know as Ear Clipping that uses triangulation to create triangles between points that can later be filled to create roofs. 
      }
    \end{itemize}
