\subsubsection{Problems}


\subsubsection{Proposed Solutions}


\subsubsection{Reflections}

    This week was mostly spent on improving the current functionality of the simulator. A couple new features were added which include trams and a new menu in the UI. 

    Since the project is moving towards the end, a lot of time was spent on the report, which added a couple new sections in the introduction, theory, and methods chapters.

\subsubsection{Meetings}

    There was a non-supervised meeting this week on Tuesday, where we met as a group to decide what needed to be worked on this week. Since the Monday counted as a weekend because of Easter, the weekly supervisor meeting was canceled.

\subsubsection{Interim Goals}

    


\subsubsection{Description of Individual Performance}
    \begin{itemize}
      \item \performance{\martin}{
        This week I did not have much time to work with and have mainly done touch ups on different areas of UI and found a method to have run-time draggable visual elements.
      }
      
      \item \performance{\felix}{
        Wrote on the theory section and introduction section. Some further bug fixing with regards to ui and camera. Also programmed features for the user interface. Wrote the user participant consent form.
      }
      
      \item \performance{\hannes}{
        This week I implemented trams, rails, indicator lights, brake lights and started refactoring intersections. I also wrote about road generation.
      }
      
      \item \performance{\marcus}{
        This week I wasn't able to work much as I was very sick for the entire week, but I improved the braking logic so that cars can have different speeds, and not just the one speed we found where everything worked well. I also made the intersection size dynamic so they are bigger if the roads have more lanes. Finally I wrote more about bezier curves on the report, following the feedback we got during the peer review meeting. During the easter week I also worked and made changes to the performance mode as well as improved the vehicle yielding behaviour.
      }
      
      \item \performance{\jakob}{
        This week I wasn't able to work as much as I would have wanted to. However, I did write about 2 sections in the report and started improving the car spawner because of some new bugs that had appeared. I also worked on the first MVP build, and updated an old car model to function with our current version of the code.
      }
    \end{itemize}
