\subsubsection{Problems}


\subsubsection{Proposed Solutions}


\subsubsection{Reflections}

    Since the report was due next week, a lot of focus was to clean up the Masthugget scene, and add details. The reason for this was to allow us to be able to take nice pictures that can be used in the report.

    Furthermore, a lot of time was also spent on improving the core stability and functionality of the simulation.

    Lastly, the final report was finished and reviewed.

\subsubsection{Meetings}

    The only meeting was the regular scheduled supervisor meeting on Monday.

\subsubsection{Interim Goals}


\subsubsection{Description of Individual Performance}
    \begin{itemize}
      \item \performance{\martin}{
        This week I mainly worked on finishing the UI and the report. I made a lot of "small" improvements/changes, improved the look quite a bit and switched the scene loading to be async. 
      }
      
      \item \performance{\felix}{
        Worked on UI and setting up the graph, and various diverse bug fixes. Also wrote on the report and adjusted to supervisor feedback and wrote meta texts for a lot of sections.
      }
      
      \item \performance{\hannes}{
        This week I implemented terrain generation from OSM. I also added steering wheels, parking signs and general bug fixes. I also wrote on the report.
      }
      
      \item \performance{\marcus}{
        This week I wrote a lot on the report, mainly about user testing and POIs. In addition, I also changed the camera behaviours, adding mouse control for the rotation and reworking how the different cameras behave. Finally, I fixed a lot of bugs in order to get a stable result.
      }
      
      \item \performance{\jakob}{
        This week I wrote a lot on the report, created a benchmarking script, did some testing, and started rewriting the carspawner again to increase its stability.
      }
    \end{itemize}
