\subsubsection{Problems}


\subsubsection{Proposed Solutions}


\subsubsection{Reflections}

    

\subsubsection{Meetings}

    The supervisor meeting was canceled for the week. In its place, the group had a meeting on their own on Monday, to review the final report before submission. Additionally, there was a meeting on Tuesday to plan the video assignment.

\subsubsection{Interim Goals}


\subsubsection{Description of Individual Performance}
    \begin{itemize}
      \item \performance{\martin}{

      }
      
      \item \performance{\felix}{
        Wrote on the report a lot, made corrections and added a bunch of text. Also set up some simulation environment to film the project in.
      }
      
      \item \performance{\hannes}{
        This week I wrote a lot on the report. I also helped with creating the movie.
      }
      
      \item \performance{\marcus}{
        This week I read through our report, fixing spelling and improving sentences. I also wrote the contribution report, and spent a lot of time gathering content for the film and editing it. In addition, I fixed the vehicle outlines and updated the cameras and their names to be in line with their functions.
      }
      
      \item \performance{\jakob}{
        This week was a hectic week, because of the assignments that had their due dates. I spent the entire Monday on finishing the report, reviewing it, and checking for grammar/spelling errors. On Tuesday and Wednesday, I spent my time working on the video assignment, which included recording videos and voice over. Then for the rest of the week, I watched the other groups videos and answered the quizzes.
      }
    \end{itemize}
