\subsubsection{Problems}


\subsubsection{Proposed Solutions}


\subsubsection{Reflections}

    

\subsubsection{Meetings}
    There was the scheduled Monday meeting with our supervisor, as well as the Chalmers Library meeting where we got information about finding information and looking for references.

\subsubsection{Interim Goals}


\subsubsection{Description of Individual Performance}
    \begin{itemize}
      \item \performance{\martin}{
        This week I worked on reworking a lot of performance logic and fixing bugs that had to do with the driving itself.
      }
      
      \item \performance{\felix}{
      Been working on programming features that allows the user to interact with objects in the simulation.
      }
      
      \item \performance{\hannes}{
      This week I fixed a lot of bugs, finished implementing the traffic stopping logic and continued working on connecting roads.
      }
      
      \item \performance{\marcus}{
        This week I worked on fixing several bugs, mainly related to how the car drives and navigates. Then I started working on refactoring the AutoDrive script that controls the cars, making it modular and much easier to add new features to and modify the current behaviour. I also attended the meeting at the library, discussing how we can find references and noted the resources we were shown.
      }
      
      \item \performance{\jakob}{
        As was decided during the weeks sprint planning meeting, the main focus was bug/error fixing. While solving bugs I created a custom editor for our AutoDrive script, which allows the user to update settings live while the simulation is running. This solved a bug which revolved around switching the navigation path/target on/off while the simulation was running. Another bug I started working on was our CarSpawner script which needed to be updated since I wrote it a couple weeks ago. This is because of our additional features of the simulator, that did not exist when I wrote it originally.
      }
    \end{itemize}
