\subsection{Project role}
In the beginning of the project i was assigned the role of adjustor. This gave me the responsibility to review all the meeting notices and check for errors.
    
\subsection{Tasks}
    During the project I was the lead developer for the navigational system, the intersection creation logic and OSM map generation. For the navigational system I created a system that creates the logical instructions the agents need to travel to a given position. For the intersection creation, I added the logic to detect when roads intersect with each other and then create intersection at that position. Lastly I implemented OSM generation support. This adds the possibility to give a OSM file as an input and the simulation will generate the map with real world roads, buildings and natural features.
    Other major features i added was the ability to connect roads to each other, trams and tram rails, procedurally generated traffic signs, one way road support. Other than that a lot of time was spend helping out with other areas and bug fixing.


\subsection{Report}
    \begin{table}[ht]
        \centering
        \begin{tabular}{cc}
            \begin{tabular}{|c|c|c|}
                %% ----- >>> HEADERS -----
                \hline
                \textbf{Section number} & \textbf{Section name} & \textbf{Co-author}
                \\\hline
                %% ----- <<< HEADERS -----
                %% ----- >>> VALUES -----
                2.2.1 & Cubic Bézier Curve & Marcus Schagerberg
                \\\hline
                2.2.4 & Composite Bézier curve & Marcus Schagerberg
                \\\hline
                2.3 & A* Algorithm & Felix Jönsson
                \\\hline
                3.2.1 & Road Generation & 
                \\\hline
                3.2.3 & ABM & 
                \\\hline
                3.2.5 & Navigation & 
                \\\hline
                3.2.6 & OpenStreetMap integration & 
                \\\hline
                5.5.1 & Performance Benchmarks & 

                
                %% ----- <<< VALUES -----
                \\\hline
            \end{tabular}
            
            \\
        \end{tabular}
        \caption{Hannes's authored project report sections}
        \label{Tab:jakob-authored-sections}
    \end{table}