\subsection{Project role}
    In the beginning of the project I was assigned the role of supervisor contact. However, during the project, the roles responsibility increased due to a team member leaving. The new responsibility included keeping contact and booking meetings with the "fackspråk" division at the Chalmers library.
    
\subsection{Tasks}
    I contributed to most parts of the simulation tool in some way. Everything from modeling physics for the vehicles, designing the UI, and working on the OpenStreetMaps(OSM) implementation. More importantly, I was the lead developer of the vehicle spawning functionality in the simulation tool. It was a script called Carspawner that I began working in the earlier stages of the project, and that I tweaked and improved a few times to adapt it all the new features that were implemented throughout the project. 
    
    Some other notable things I created in the simulation would be,

    \begin{itemize}
        \item \textbf{TimeManager} - A script that handles time based events based on the in game time. Implemented using a calendar queue. An example, would be the buses that use it to follow their schedules.
        \item \textbf{Benchmarker} - A script that was used to perform performance benchmarks.
        \item \textbf{Traffic Lights} - The spawning of traffic lights in intersections, and the needed logic for them to function.
        \item \textbf{OSM Roofs} - Since OSM data only supplies the coordinate locations of the corners of buildings, I had to implement triangulation by ear clipping to create the roofs of each building.
        
    \end{itemize}

    This summarizes the main areas that I contributed with to the project, but not every detail due to the scale of the project. 

\subsection{Report}
    For the report I wrote mostly in methods, results, discussion and conclusion. Table \ref{Tab:jakob-authored-sections} below displays all the section I wrote by myself, one being co-authored with Marcus Schagerberg. Not included in the table, I also wrote some of the meta texts in the report. Lastly, I spent a lot of time towards the end of the project to spell check and fix grammars in the entire report. 
    
    \begin{table}[ht]
        \centering
        \begin{tabular}{cc}
            \begin{tabular}{|c|c|c|}
                %% ----- >>> HEADERS -----
                \hline
                \textbf{Section number} & \textbf{Section name} & \textbf{Co-author}
                \\\hline
                %% ----- <<< HEADERS -----
                %% ----- >>> VALUES -----
                
                3.1.1 & Unity & Martin Blom
                \\\hline
                3.1.2 & Third-party Assets & 
                \\\hline
                3.1.3 & GitHub & 
                \\\hline
                3.3.1 & Quality vs Performance & 
                \\\hline
                3.3.2 & Optimization & 
                \\\hline
                3.4.1 & Design & 
                \\\hline
                3.5.2 & Trello & Felix Jönsson
                \\\hline
                4.1 & Final Product & 
                \\\hline
                5.1 & Performance Evaluation & 
                \\\hline
                5.4 & Development Process & 
                \\\hline
                5.5.1 & Road and Intersection Types & Marcus Schagerberg
                \\\hline
                5.5.2 & OSM & 
                \\\hline
                5.5.3 & Vehicle Types &
                \\\hline
                6.3 & Future Usage of the Simulation &
                \\\hline
                6.4 & Learning Outcome &
                
                %% ----- <<< VALUES -----
                \\\hline
            \end{tabular}
            
            \\
        \end{tabular}
        \caption{Jakob's authored project report sections}
        \label{Tab:jakob-authored-sections}
    \end{table}