

\subsection{Project role}
    In the project I was assigned project leader, with the main responsibility of planning our work over a longer time period. We employed the scrum framework and worked in sprints of one week. My role involved planning ahead, deciding during which sprint work should be done and adapting the upcoming sprints based on the circumstances. It was then the responsibility of Felix to plan that work for one sprint at the time, managing the tasks and Trello board to ensure that we reached the sprint goals.

    The work I planned and distributed for the sprints was based on the intermediate goals set by the group as a whole during planning meetings. There, it was decided what the next goal should be and when to place the deadline. These goals usually revolved either around project report handins, or iteration versions where it was described what the new version of the tool should be capable of.
    
\subsection{Tasks}
    In the project I was the main developer for AutoDrive, our automatic driving implementation, RoadGenerator, the tool for creating roads the vehicles could follow, as well as the algorithm for the vehicles to be able to navigate intersections. In AutoDrive, I worked on the algorithms for steering the vehicles along the lanes as well as handling their acceleration and braking including the detection of targets they need to brake for. For AutoDrive, I also wrote the performance mode which uses a much simpler physics engine I wrote. This in comparison to the quality mode which is more realistic, but also significantly more performance heavy, due to the use of the realistic vehicle physics engine in the Edy's Vehicle Physics asset. I also assisted Hannes in the generation of intersections, and vehicle navigation that allows them to find their way around the road system. My main areas were very logic heavy, meaning a lot of time was spent developing the logic as well as debugging and improving it. 

\subsection{Report}
    In the report, I mainly wrote about Bézier curves and the sections about the areas of my development. I also wrote about user testing and the results from my user testing session. I also set up the LaTeX workspace with all the commands and file structure as well as repository connection. In Table \ref{Tab:marcus-authored-sections}, a detailed list of the sections I have written is compiled, together with any co-authors.

    \begin{table}[ht]
        \centering
            \begin{tabular}{|c|c|c|}
                %% ----- >>> HEADERS -----
                \hline
                \textbf{Section number} & \textbf{Section name} & \textbf{Co-author}
                \\\hline
                %% ----- <<< HEADERS -----
                %% ----- >>> VALUES -----
                N/A & Abstract & Martin Blom
                \\\hline
                N/A & Sammandrag & Martin Blom
                \\\hline
                N/A & Acknowledgements &
                \\\hline
                2.2 & Bézier curves &
                \\\hline
                2.2.1 & Cubic Bézier Curve & Hannes Kaulio
                \\\hline
                2.2.2 & De Casteljau's algorithm &
                \\\hline
                2.2.3 & Bézier Clipping &
                \\\hline
                2.2.4 & Composite Bézier curve & Hannes Kaulio
                \\\hline
                2.4 & Procedural mesh generation &
                \\\hline
                3.2.2 & Points of Interest &
                \\\hline
                3.2.4 & Vehicle Driving Implementation &
                \\\hline
                3.5.3 & Code Reviewing &
                \\\hline
                3.6 & Testing &
                \\\hline
                4.2 & Performance &
                \\\hline
                4.3.1 & Experienced Tester &
                \\\hline
                5.2 & Unreached Goals &
                \\\hline
                5.3.2 & Changes made based on the user testing feedback &
                \\\hline
                5.5.1 & Road and Intersection Types, last paragraph &
                \\\hline
                5.5.4 & Performance Optimisation &
                \\\hline
                5.5.5 & Simulation Improvements &
                \\\hline
                6.2 & Future Problem Presentations &
                
                %% ----- <<< VALUES -----
                \\\hline
            \end{tabular}
        \caption{Marcus's authored project report sections}
        \label{Tab:marcus-authored-sections}
    \end{table}