\subsection{Project role}
In the project I was assigned the role of secretary, this meant having the responsibility for things such as sending out meeting notices, taking meeting minutes and documenting various stuff.

\subsection{Tasks}
In the project I was the head developer of the UI. I produced the starting menu UI as well as the overlay UI with the exception of the statistics window. In both parts I was responsible for the design as well as creating and connecting (controller script) most of the interactive things to their respective functionality. I also developed the audio system and it's functionality to adjust the volume within the settings menu. Both the menu UI controller and the overlay UI controller contains functionality to load a new scene asynchronously and unload their scene together with unsubscribing to the right events. In the earlier stages of the project I also contributed to the large AutoDrive script by working on the road occupation for cars, as well as the performance mode and the development tool used to visualize different car targets. During the development I also got the responsibility to create the first MVP scene for demos.

Outside of contributions to the project, me and Felix created all the material for, and executed the mid term presentation. We also got appointed to the task of doing the last group opposition while the rest of the team does the final presentation. I also contributed to the making of the movie by recording a portion of the scenes.

\subsection{Report}
    
     \begin{table}[ht]
        \centering
            \begin{tabular}{|c|c|c|}
                %% ----- >>> HEADERS -----
                \hline
                \textbf{Section number} & \textbf{Section name} & \textbf{Co-author}
                \\\hline
                %% ----- <<< HEADERS -----
                %% ----- >>> VALUES -----
                N/A & Abstract & Marcus Schagerberg
                \\\hline
                N/A & Sammandrag & Marcus Schagerberg
                \\\hline
                1.1 & Background &
                \\\hline
                3.1 & Tools & Jakob Windt
                \\\hline
                3.1.1 & Unity & Jakob Windt
                \\\hline
                3.4.2 & Statistics &
                \\\hline
                3.5 & Workflow & 
                \\\hline
                3.5.1 & Weekly Sprints &
                \\\hline
                5.0 & Discussion(meta text) &
                \\\hline
                5.5 & Future Improvments &
                \\\hline
                5.5.6 & Statistics &
                \\\hline
                5.5.7 & Map Editor &
                \\\hline
                6.1 & Additional Knowledge &
                
                %% ----- <<< VALUES -----
                \\\hline
            \end{tabular}
        \caption{Martin's authored project report sections}
        \label{Tab:marcus-authored-sections}
    \end{table}