\noindent
\label{itm:a*}\textbf{A*}: A popular graph traversal and path finding algorithm due to its completeness and optimal efficiency. A* is used to find the shortest possible path from one node to another.

\noindent
\label{itm:agent}\textbf{Agent}: Autonomous entities that inhabits an environment and act based on predefined rules.

\noindent
\label{itm:abm}\textbf{Agent Based Model (ABM)}: A computer simulation model in which agents interact with each other and their environment to produce emergent behavior. 

\noindent
\label{itm:csharp}\textbf{C\#}: C\# is a general purpose programming language developed by Microsoft. C\# is pronounced "C sharp" and belongs to the programming language family of C.

\noindent
\label{itm:c++}\textbf{C++}: One of the most popular general purpose programming languages. C++ belongs to the programming language family of C, with the major distinction from C that C++ is an object oriented language.

\noindent
\label{itm:data-structure}\textbf{Data Structure}: A way of organizing and storing data in a computer so that it can be accessed, manipulated, and modified efficiently. Some common examples are arrays, stacks, and linked lists.

\noindent
\label{itm:fps}\textbf{FPS}: Frames Per Second, is a unit used for measuring software performance, usually in games. It is the number of images displayed per second. A higher FPS results in a smoother experience.

\noindent
\label{itm:information-visualization}\textbf{Information Visualization}: Field that focuses on creating meaningful and easy to interpret graphical representations of data.

\noindent
\label{itm:monobehaviour}\textbf{MonoBehaviour}: Base class for Unity scripts applied to in-game objects. Provides access to event functions and other predefined functionality used by the objects.

\noindent
\label{itm:open-street-map}\textbf{OSM}: OpenStreetMap is an open source database containing real world map data.

\noindent
\label{itm:pooling}\textbf{Pooling}: A technique used in programming to improve performance by reusing objects instead of creating new ones. 

\noindent
\label{itm:prefab}\textbf{Prefab}: A reusable object in Unity that stores a configuration and can be used as a template for creating assets.

\noindent
\label{itm:repository}\textbf{Repository}: A repository acts as a container that stores a project's files and their individual revision history.

\noindent
\label{itm:scrum}\textbf{Scrum}: The scrum agile project management framework provides structure and instructions for management of work and is popular among software development teams.

\noindent 
\label{itm:scrum-boards}\textbf{Scrum-board}: A bulletin board used for tracking tasks and planning development.

\noindent
\label{itm:story}\textbf{Story}: In the scrum framework, a story is essentially a set of tasks that will result in a new or updated desired functionality/product.  

\noindent
\label{itm:ui}\textbf{UI}: UI, or User Interface, is the connection between humans and computers. It determines how the user interacts with the program.

\noindent
\label{itm:unity}\textbf{Unity}: A cross-platform game engine used to develop games.

\noindent
\label{itm:unity-asset}\textbf{Unity Asset}: A file  containing reusable content that can be imported into Unity projects. Can be accessed through Unity's official platform or imported via third-party repositories. 

\noindent
\label{itm:user-testing}\textbf{User Testing}: A method of testing and evaluating a product by observing and gathering data from real users. 

\noindent
\label{itm:ux}\textbf{UX}: UX, or User Experience, refers to the overall experience for someone using a product. The goal of good UX design is to create intuitive and enjoyable products.

\noindent
\label{itm:pr}\textbf{Pull Request}: A pull request is a built in request to merge code from one branch into another in Git

\noindent
\label{itm:api}\textbf{API}: API, or Application Programming Interface, is a way for different programs to communicate and send data to each other

