% UPDATED BY MARCUS SCHAGERBERG, 2023
% CREATED BY WOLFGANG AHRENDT, 2021


\section{Unity}
Unity is a cross-platform game engine used to create both 2D and 3D games. Unity supports a lot of features that speed up development time. 

\input{modules/theory/bezier_curves}

% Hannes Kaulio
\section{A* Algorithm}
    A* is an algorithm widely used for path finding and graph traversal \cite{A-Star-Algorithm}. It is classified as an informed search algorithm since it greedily explores the path finding environment by taking into account both the cost of the path from the starting node to the one that is currently being explored, as well as a heuristic function that estimates the distance between the currently explored node and the goal node. Given a start, and end node in a weighted graph, the algorithm will find the shortest path between the nodes. Together, these two forms an estimate function of the best path towards the goal. Given that A* is complete under the precondition that the search space is finite, and that the branching factor is finite as well, this guarantees that if a path exist, it will be found. Furthermore, if some additional conditions are fulfilled with regards to the heuristic function, A* can be guaranteed to return an optimal path. For this to be the case, the heuristic function needs to admissible or consistent, since a consistent function is also by definition, admissible. 

\input{modules/theory/mesh_generation}

\section{Scrum and Agile Software Development}
Agile Software Development is a software development framework which emphasizes vertical development cycles, where software should be delivered frequently in atomic slices to enable quick feedback and high flexibility with regards to how the product develops. When developing complex products, and especially when the development team has not worked on anything similar to the current developed product, implementing an Agile framework can be particularly important. Since features is delivered in small complete chunks, this minimizes the investment risk compared to a more horizontal feature development. 

\section{ABM}

