\documentclass{article}
\usepackage{../../preamble}
\usepackage{minutes_preamble}
\usepackage{fancyhdr}


%%%%% Update this each meeting %%%%%
\newcommand{\meetingdate}{2023-01-23}
\newcommand{\meetingtime}{14:00}
\newcommand{\meetingplace}{EG2515}
\newcommand{\meetingname}{Supervisor meeting}
\newcommand{\secretary}{\martin}
\newcommand{\adjuster}{\hannes}
\newcommand{\attendees}{\martin \and \felix \and \hannes \and \marcus \and \jakob}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



  
\begin{document}
    %!!!!! Do not touch !!!!!%
    \begin{titlepage}
        \settitle{\meetingname}
        \date{\meetingdate}
        \maketitle
        
        \thispagestyle{first}
        
        \timeanddate{\meetingdate \space \meetingtime}
        \place{\meetingplace}
        \called{\members}
        \attended{\attendees}
    \end{titlepage}
    \newpage
    \pagestyle{fancy}
    %!!!!!!!!!!!!!!!!!!!!!!!!%

    %%%%% Meeting protocol %%%%%
    \section{Opening}
        Everyone introduced themselves.

    \section{Approval of previous minutes}
        \approve{\hannes}
        
    \section{Notes}
        \begin{itemize}
            \item A* search algorithm
            \item Individual scenes
        \end{itemize}

    \section{Discussion}
        Discussions around data collection. Emission, congestion points and meeting deadlines were mentioned. Everyone agreed on getting the basics down first as a staring point. Maybe use A* to begin with. Try to really break down tasks. Use full UI for changing parameters in the simulation. Testing Internally: A few members weekly make a build of the project and test it for an hour or so, then document the experience. Use individual scenes and work with prefabs to make version control easier. Use branches for different tools to make tracking bugs and working on multiple things easier.

    \section{Decisions}
        \begin{itemize}
            \item Weekly meetings on Monday at 3:00 PM to start with.
            \item Send email with necessary information to Natasha.
        \end{itemize}
    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
